Survey paper tables and figures

### 2021-09-20 survey/code/paper-tables.Rmd
Tidy up code and figures
1. Convert everything to put figures in the right directory.

2. Use consistent population data.

3. Move legends on contacts plot so the plots have consistent x axes.

4. Finish signal time series plot.

@@

```{r demo-region}
data %>%
  select(fips, weight) %>%
  mutate(
    fips = ifelse(is.na(fips), NA_character_, sprintf("%05d", fips)),
    state_abbr = toupper(name_to_abbr(state_fips_to_name(fips)))) %>%
  inner_join(select(state_census, REGION, ABBR),
             by = c("state_abbr" =  "ABBR")) %>%
  mutate(REGION = case_when(
    REGION == 1 ~ "Northeast",
    REGION == 2 ~ "Midwest",
    REGION == 3 ~ "South",
    REGION == 4 ~ "West"
  )) %>%
  proportionate(REGION) %>%
  kable(col.names = c("Region", "Number", "Unweighted %", "Weighted %"),
        digits = 1, format.args = list(big.mark = ","))
```

@@

### Tested given symptoms

@@

Now plot:

@@

ggsave("figures/symptoms-comparison.pdf")
```

@@

Based on code from Minttu Rönn.

@@

```{r case-rate-compare}
# State adult populations, from Census data
state_pops <- read.csv("state-age-pops.csv")
# State-level age distributions of cases, from CDC data
case_age_dist <- read.csv("case-age-distribution.csv")

@@

state_case_compare <- data %>%
  filter(!is.na(fips)) %>%
  mutate(
    ever_pos = case_when(
      B10a == "1" ~ TRUE,
      B11 == "1" ~ TRUE,
      B11 == "2" ~ FALSE,
      B8 == "2" ~ FALSE,
      TRUE ~ NA
    ),
    week = floor_date(as.Date(StartDatetime), unit = "week"),
    fips = sprintf("%05d", fips),
    state_abbr = name_to_abbr(state_fips_to_name(fips))
  ) %>%
  group_by(week, state_abbr) %>%
  summarize(ever_pos = 100 * weighted.mean(ever_pos, weight, na.rm = TRUE),
            .groups = "drop") %>%
  left_join(state_case_rate,
            by = c("state_abbr" = "state", "week" = "time_value"))

@@

ggsave("figures/cumulative-case-compare.pdf", g, width = 10, height = 7)

@@

```{r}
max(state_case_compare$week)

@@

Based on code from Alyssa Bilinski.

@@

pops <- read.csv("data/population.csv")

# SVI
svi <- read.csv("data/SVI2018_US_COUNTY.csv") %>%
  mutate(SVI_cat = case_when(RPL_THEMES >= 0.75 ~ "1st quartile",
                             RPL_THEMES >= 0.5 & RPL_THEMES < 0.75 ~ "2nd quartile",
                             RPL_THEMES >= 0.25 & RPL_THEMES < 0.5 ~ "3rd quartile",
                             RPL_THEMES < 0.25 ~ "4th quartile")) %>%
  select(FIPS, SVI_cat)
```

@@

```{r contacts-data}
contacts_data <- data %>%
  # Exclude ludicrous numbers of contacts, since they screw up the means
  filter(chk_work_contacts & chk_shopping_contacts & chk_social_contacts & chk_other_contacts) %>%
  mutate(
    C13 = ifelse(!is.na(C13), C13, C13b), # Replaced in Wave 10; treat as identical
    C14 = ifelse(!is.na(C14), C14, C14a), # Replaced in Wave 8; treat as identical
    C13_options = split_options(C13),
    state = state_fips_to_name(ifelse(is.na(fips), NA_character_, sprintf("%05d", fips))),
    week = floor_date(as.Date(StartDatetime), unit = "week"),
    any_work = ifelse(is.na(C10_1_1), 0, C10_1_1),
    any_shopping = ifelse(is.na(C10_2_1), 0, C10_2_1),
    any_social = ifelse(is.na(C10_3_1), 0, C10_3_1),
    any_other = ifelse(is.na(C10_4_1), 0, C10_4_1),
    chk = !is.na(C10_1_1) | !is.na(C10_2_1) | !is.na(C10_3_1) | !is.na(C10_4_1),
    work_mod2 = ifelse(chk, any_work, NA),
    social_mod2 = ifelse(chk, any_social, NA),
    shopping_mod2 = ifelse(chk, any_shopping, NA),
    other_mod2 = ifelse(chk, any_other, NA),
    contacts_tot = (as.numeric(work_mod2) + as.numeric(shopping_mod2) +
                      as.numeric(social_mod2) + as.numeric(other_mod2)),
    age_cat = case_when(D2 <= 2 ~ "18-34",
                        D2 %in% 3:5 ~ "35-64",
                        D2 > 5 ~ "65+")
  ) %>%
  left_join(svi, by = c("fips" = "FIPS")) %>%
  left_join(pops, by = c("state" = "StateName"))
```

@@

# TODO See if we can merge these into one big facet_grid so the widths match
# (not sure how to deal with legends?)
a <- ggplot(g1, aes(x = week, y = value, col = SVI_cat, group = SVI_cat)) +
  geom_line() +
  facet_wrap(. ~ var_cat, scales = "free", ncol = 4) +
  scale_color_discrete(name = "SVI") +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %Y",
               date_minor_breaks = "1 month") +
  labs(x = "", y = "") +
  ylim(0,  NA) +
  theme_bw()

b <- ggplot(g2, aes(x = week, y = value, col = age_cat, group = age_cat)) +
  geom_line() +
  facet_wrap(. ~ var_cat, scales = "free", ncol = 4) +
  scale_color_discrete(name = "Age") +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %Y",
               date_minor_breaks = "1 month") +
  labs(x = "", y = "") +
  ylim(0, NA) +
  theme_bw()

c <- ggplot(g3, aes(x = week, y = value, col = region, group = region)) +
  geom_line() +
  facet_wrap(.~var_cat, scales = "free", ncol = 4) +
  scale_color_discrete(name = "Region")  +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %Y",
               date_minor_breaks = "1 month") +
  labs(x = "", y = "") +
  ylim(0, NA) +
  theme_bw()

@@

ggsave("figures/contacts-masks-transport.pdf", g, width = 8, height = 5)
```

@@

Based on code from Marissa Reitsma.

```{r vaccine-hesitancy-map}
# Get data into the form Marissa's code expects
df <- data %>%
  select(StartDatetime, fips, V1, V3, weight) %>%
  mutate(date = as.Date(StartDatetime)) %>%
  filter(!is.na(fips),
         date >= as.Date("2021-03-01"),
         date <= as.Date("2021-04-05")) %>%
  mutate(
    hesitant = case_when(
      V1 == 1 ~ FALSE,
      V3 %in% 1:2 ~ FALSE,
      V3 %in% 3:4 ~ TRUE),
    fips = sprintf("%05d", fips))

@@

ggsave("figures/hesitancy-county-map.pdf", g, width = 6, height = 4)

>>>>

Some essential cleaning. We use 5-digit FIPS codes with leading zeros by
convention, and we'll want region names for plots:

```{r clean-data}
data$fips <- ifelse(is.na(data$fips), NA_character_, sprintf("%05d", data$fips))

state_census$REGION <- case_when(
  state_census$REGION == 1 ~ "Northeast",
  state_census$REGION == 2 ~ "Midwest",
  state_census$REGION == 3 ~ "South",
  state_census$REGION == 4 ~ "West"
)
```

@@

```{r demo-region}
data %>%
  select(fips, weight) %>%
  mutate(state_abbr = toupper(name_to_abbr(state_fips_to_name(fips)))) %>%
  inner_join(select(state_census, REGION, ABBR),
             by = c("state_abbr" =  "ABBR")) %>%
  proportionate(REGION) %>%
  kable(col.names = c("Region", "Number", "Unweighted %", "Weighted %"),
        digits = 1, format.args = list(big.mark = ","))
```

@@

## Trends in each signal, by Census region

Figure 2:

```{r signal-anosmia-trends, message=FALSE}
gc()

start_day <- "2020-04-06"
end_day <- "2021-04-05"

anosmia <- data %>%
  select(StartDatetime, B2, fips, weight) %>%
  filter(!is.na(fips)) %>%
  mutate(date = as.Date(StartDatetime),
         anosmia = is_selected(split_options(B2), "13"),
         state = toupper(name_to_abbr(state_fips_to_name(fips)))) %>%
  group_by(date, state) %>%
  summarize(anosmia = 100 * weighted.mean(anosmia, weight, na.rm = TRUE),
            sample_size = sum(!is.na(anosmia))) %>%
  select(time_value = date, value = anosmia, geo_value = state, sample_size) %>%
  as.covidcast_signal(signal = "anosmia", geo_type = "state")

signals <- covidcast_signals(
  c("fb-survey", "fb-survey", "jhu-csse", "hhs", "jhu-csse"),
  c("raw_wcli", "raw_whh_cmnty_cli", "confirmed_incidence_prop",
    "confirmed_admissions_covid_1d_prop", "deaths_incidence_prop"),
  start_day, end_day,
  geo_type = "state")

signals <- append(signals, list(anosmia)) %>%
  aggregate_signals(format = "long")

signals$signal <- factor(
  signals$signal,
  levels = c("anosmia", "raw_wcli", "raw_whh_cmnty_cli", "confirmed_incidence_prop",
             "confirmed_admissions_covid_1d_prop", "deaths_incidence_prop"),
  labels = c("Anosmia %", "CLI %", "Community CLI %", "Cases per 100,000",
             "Hospitalizations per 100,000", "Deaths per 100,000"))

to_plot <- signals %>%
  mutate(geo_value = toupper(geo_value)) %>%
  inner_join(select(state_census, ABBR, REGION, POPESTIMATE2019),
             by = c("geo_value" = "ABBR")) %>%
  group_by(REGION, time_value, signal) %>%
  summarize(value = weighted.mean(value,
                                  ifelse(data_source %in% c("jhu-csse", "hhs"),
                                         POPESTIMATE2019, sample_size),
                                  na.rm = TRUE))

to_plot <- to_plot %>%
  filter(REGION != "X") %>%
  group_by(REGION, signal) %>%
  arrange(time_value) %>%
  mutate(value = rollmean(value, 7, fill = NA))

ggplot(to_plot, aes(x = time_value, y = value, color = REGION)) +
  geom_line() +
  facet_wrap(vars(signal), nrow = 2, ncol = 3, scales = "free_y") +
  labs(x = "Date", y = "Value", color = "Census Region") +
  scale_x_date(date_breaks = "3 months",
               date_labels = "%b %Y",
               date_minor_breaks = "1 month",
               guide = guide_axis(angle = 45)) +
  theme_bw() +
  theme(legend.position = "bottom")

ggsave("../paper/fig/signal-time-series.pdf",
       width = 7, height = 5)
```

@@

Now plot (Figure 1):

@@

ggsave("../paper/fig/symptoms-comparison.pdf")
```

@@

Figure 3. Based on code from Minttu Rönn.

@@

```{r case-rate-compare, message=FALSE}
# Estimates of the Total Resident Population and Resident Population Age 18
# Years and Older for the United States, States, and Puerto Rico: July 1, 2019
# (SCPRC-EST2019-18+POP-RES)
state_pops <- read.csv("state-age-pops.csv")

# State-level age distributions of cases, from CDC data
case_age_dist <- read.csv("case-age-distribution.csv")

@@

state_case_compare <- data %>%
  filter(!is.na(fips)) %>%
  mutate(
    ever_pos = case_when(
      B10a == "1" ~ TRUE,
      B11 == "1" ~ TRUE,
      B11 == "2" ~ FALSE,
      B8 == "2" ~ FALSE,
      TRUE ~ NA
    ),
    week = floor_date(as.Date(StartDatetime), unit = "week"),
    state_abbr = name_to_abbr(state_fips_to_name(fips))
  ) %>%
  group_by(week, state_abbr) %>%
  summarize(ever_pos = 100 * weighted.mean(ever_pos, weight, na.rm = TRUE),
            .groups = "drop") %>%
  left_join(state_case_rate,
            by = c("state_abbr" = "state", "week" = "time_value"))

@@

ggsave("../paper/fig/cumulative-case-compare.pdf", g, width = 10, height = 7)

@@

```{r case-rate-correlations}
max(state_case_compare$week)

@@

Figure 4. Based on code from Alyssa Bilinski.

@@

# We don't actually need populations -- just region codes
pops <- state_census %>%
  select(state = NAME, region = REGION)

# SVI
svi <- read.csv("data/SVI2018_US_COUNTY.csv") %>%
  mutate(SVI_cat = case_when(RPL_THEMES >= 0.75 ~ "1st quartile",
                             RPL_THEMES >= 0.5 & RPL_THEMES < 0.75 ~ "2nd quartile",
                             RPL_THEMES >= 0.25 & RPL_THEMES < 0.5 ~ "3rd quartile",
                             RPL_THEMES < 0.25 ~ "4th quartile"),
         FIPS = sprintf("%05d", FIPS)) %>%
  select(FIPS, SVI_cat)
```

@@

```{r contacts-data}
contacts_data <- data %>%
  # Exclude ludicrous numbers of contacts, since they screw up the means
  filter(chk_work_contacts & chk_shopping_contacts & chk_social_contacts & chk_other_contacts) %>%
  mutate(
    C13 = ifelse(!is.na(C13), C13, C13b), # Replaced in Wave 10; treat as identical
    C14 = ifelse(!is.na(C14), C14, C14a), # Replaced in Wave 8; treat as identical
    C13_options = split_options(C13),
    state = state_fips_to_name(fips),
    week = floor_date(as.Date(StartDatetime), unit = "week"),
    any_work = ifelse(is.na(C10_1_1), 0, C10_1_1),
    any_shopping = ifelse(is.na(C10_2_1), 0, C10_2_1),
    any_social = ifelse(is.na(C10_3_1), 0, C10_3_1),
    any_other = ifelse(is.na(C10_4_1), 0, C10_4_1),
    chk = !is.na(C10_1_1) | !is.na(C10_2_1) | !is.na(C10_3_1) | !is.na(C10_4_1),
    work_mod2 = ifelse(chk, any_work, NA),
    social_mod2 = ifelse(chk, any_social, NA),
    shopping_mod2 = ifelse(chk, any_shopping, NA),
    other_mod2 = ifelse(chk, any_other, NA),
    contacts_tot = (as.numeric(work_mod2) + as.numeric(shopping_mod2) +
                      as.numeric(social_mod2) + as.numeric(other_mod2)),
    age_cat = case_when(D2 <= 2 ~ "18-34",
                        D2 %in% 3:5 ~ "35-64",
                        D2 > 5 ~ "65+")
  ) %>%
  left_join(svi, by = c("fips" = "FIPS")) %>%
  left_join(pops, by = c("state"))
```

@@

# Pull the legends up towards the plots to eliminate wasted space. ggplot's
# default unit is half a line height, and a line height is 11 pt, so work in
# multiples of this.
legend_top_margin <- -11 * 3 / 2

a <- ggplot(g1, aes(x = week, y = value, col = SVI_cat, group = SVI_cat)) +
  geom_line() +
  facet_wrap(. ~ var_cat, scales = "free", ncol = 4) +
  scale_color_discrete(name = "SVI") +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %Y",
               date_minor_breaks = "1 month") +
  labs(x = "", y = "") +
  ylim(0,  NA) +
  theme_bw() +
  theme(legend.position = "bottom",
        legend.margin = margin(legend_top_margin, 0, 11 / 2, 0),
        plot.margin = margin(11 / 2, 11 / 2, 0, 11 / 2))

b <- ggplot(g2, aes(x = week, y = value, col = age_cat, group = age_cat)) +
  geom_line() +
  facet_wrap(. ~ var_cat, scales = "free", ncol = 4) +
  scale_color_discrete(name = "Age") +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %Y",
               date_minor_breaks = "1 month") +
  labs(x = "", y = "") +
  ylim(0, NA) +
  theme_bw() +
  theme(legend.position = "bottom",
        legend.margin = margin(legend_top_margin, 0, 11 / 2, 0),
        plot.margin = margin(11 / 2, 11 / 2, 0, 11 / 2))

c <- ggplot(g3, aes(x = week, y = value, col = region, group = region)) +
  geom_line() +
  facet_wrap(. ~ var_cat, scales = "free", ncol = 4) +
  scale_color_discrete(name = "Region")  +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %Y",
               date_minor_breaks = "1 month") +
  labs(x = "", y = "") +
  ylim(0, NA) +
  theme_bw() +
  theme(legend.position = "bottom",
        legend.margin = margin(legend_top_margin, 0, 11 / 2, 0),
        plot.margin = margin(11 / 2, 11 / 2, 0, 11 / 2))

@@

ggsave("../paper/fig/contacts-masks-transport.pdf", g, width = 8, height = 5)
```

@@

Figure 5B. Based on code from Marissa Reitsma.

```{r vaccine-hesitancy-map}
# Get data into the form Marissa's code expects
df <- data %>%
  select(StartDatetime, fips, V1, V3, weight) %>%
  mutate(date = as.Date(StartDatetime)) %>%
  filter(!is.na(fips),
         date >= as.Date("2021-03-01"),
         date <= as.Date("2021-04-05")) %>%
  mutate(hesitant = case_when(
             V1 == 1 ~ FALSE,
             V3 %in% 1:2 ~ FALSE,
             V3 %in% 3:4 ~ TRUE))

@@

ggsave("../paper/fig/hesitancy-county-map.pdf", g, width = 6, height = 4)
